### 2018-07-02 Thesis/Parts/Future_work/Future_work.tex
Auto stash before merge of "master" and "origin/master"

\subheader{Collecting a set of terms}
Our results show that, for larger texts, TF-IDF outperforms the embeddings. Given this, it would be logical to use TF-IDF for search tasks on sets with many tokens. However, the search term itself will contain a small number of tokens, as our research showed, embeddings perform better in this situation. Future work could try to combine these findings, by collecting a large number of words, resembling the meaning (captured by the embeddings), and transforming this into a (large) collection of words (mimicking word occurrence, captured by the TF-IDF). If this could be done effectively, the power of the TF-IDF method could be applied to smaller texts. This process could be seen as a translation from word-embedding space into TF-IDF space. Furthermore, it would be interesting to see which words would be selected and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.
\end{document}

>>>>

\subheader{Collecting a set of terms}
Our results show that, for larger texts, TF-IDF outperforms the embeddings. Given this, it would be logical to use TF-IDF for search tasks on sets with many tokens. However, the search term itself will contain a small number of tokens, as our research showed, embeddings perform better in this situation. Future work could try to combine these findings, by collecting a large number of words, resembling the meaning (captured by the embeddings), and transforming this into a (large) collection of words (mimicking word occurrence, captured by the TF-IDF). If this could be done effectively, the power of the TF-IDF method could be applied to smaller texts. This process could be seen as a translation from word-embedding space into TF-IDF space. Furthermore, it would be interesting to see which words would be selected and if these words represent the given sentence as an "extracted version" which would still be interpretable by humans.

\subheader{Pre-categorization}
Our results show that the embeddings can indicate the domains of the given articles, as visualized in the journal embedding plots (Figure~\ref{figure:titlePlotNormal}-\ref{figure:abstractPlotGrouped}). This knowledge could be used to pre-process given texts, creating a two-step search. This method would first categorize the given article into a field, and then search in the limited set of journals for the best fit. This has two advantages: A) we predict the field of the article, giving additional information to a user and B) once an article is inside a certain domain, ambiguous words between domains (i.e. cloud for computer science and meteorology) are eliminated, since these embeddings do not have to be trained with the other embeddings, which create ambiguity. A possible downside of this approach is the need for data within each domain, since the embeddings are created on two levels, cross-domain for domain categorization and in-domain for journal categorization. The lack of articles within one domain could hurt the embeddings since they need training data to make accurate predictions. In a situation were there is no categorization data available, like in our research, a k-means algorithm should suffice for categorization. The goal is to have multiple separate vector spaces, for this is does not matter if the "domains" are well-interpretable or make sense to humans.
\end{document}

### 2018-07-02 Thesis/Parts/Research_results/Research_results.tex
Updated thesis
Auto stash before merge of "master" and "origin/master"

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Research results}
\subheader{Ranking}
The figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} show the result of the categorization task as ranking results. The rank indicates the position of the correct journal in the sorted list of matched journals. Figure~\ref{figure:titleRanks} shows the ranking results for the different sets based on the title. Figure~\ref{figure:abstractRanks} displays the ranking results based on the abstract. Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.\\
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_rankings}
\caption{Median and average title rankings}\label{figure:titleRanks}
\end{figure}
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Abstract_rankings}
\caption{Median and average abstract rankings}\label{figure:abstractRanks}
\end{figure}
\clearpage
\subheader{Rank distribution}
Figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show the distributions of the ranks for each set. The figures plot the summed amount of articles against the ranks on a logarithmic scale. Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract. These graphs give a detailed view of the ranks presented in their respective figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks}. The Y-axis of the two figures show the fraction of the total number of articles. The X-axis plots the ranks of the articles. These ranks are the ranks of each individual article in our validation set, in contrast to figure~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} which show average and median ranks.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_rank_distribution}
\caption{Title rank distribution per set}\label{figure:titleDistribution}
\end{figure}
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Abstract_rank_distribution}
\caption{Abstract rank distribution per set}\label{figure:abstractDistribution}
\end{figure}

>>>>

\documentclass[../../Thesis.tex]{subfiles}
\begin{document}
\header{Research results}
In this chapter the results of our research will be presented with only the required explanation of the results. These results will be discussed in Chapter 7: Discussion.
\subheader{Ranking}
The Figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} show the result of the categorization task as ranking results. The rank indicates the position of the correct journal in the sorted list of matched journals. Figure~\ref{figure:titleRanks} shows the ranking results for the different sets based on the title. Figure~\ref{figure:abstractRanks} displays the ranking results based on the abstract. Both graphs show both average and median ranks, based on the cosine-similarity between the article and journal embeddings or feature vectors.
\clearpage
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_rankings}
\caption{Median and average title rankings}\label{figure:titleRanks}
\end{figure}
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Abstract_rankings}
\caption{Median and average abstract rankings}\label{figure:abstractRanks}
\end{figure}
\clearpage
\subheader{Rank distribution}
Figures~\ref{figure:titleDistribution} \&~\ref{figure:abstractDistribution} show the distributions of the ranks for each set. The figures plot the summed amount of articles against the ranks on a logarithmic scale. Figure~\ref{figure:titleDistribution} shows the rank distribution for the titles, Figure~\ref{figure:abstractDistribution} shows this for the ranks based on the abstract. These graphs give a detailed view of the ranks presented in their respective figures~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks}. The Y-axis of the two figures show the fraction of the total number of articles. Due to this, all sets will move towards one. When one is hit, the graph stagnates since there are no more articles that can be added once the value reaches one. The X-axis plots the ranks of the articles. These ranks are the ranks of each individual article in our validation set, in contrast to figure~\ref{figure:titleRanks} \&~\ref{figure:abstractRanks} which show average and median ranks.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_rank_distribution}
\caption{Title rank distribution per set}\label{figure:titleDistribution}
\end{figure}
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Abstract_rank_distribution}
\caption{Abstract rank distribution per set}\label{figure:abstractDistribution}
\end{figure}
